Investigate co-expression issue in reprocessed RNASeq

### 2016-09-02 code/Rmd/InvestigateCoexpIssue.Rmd
Temp commit

synapseLogin()
```
### Data download
#### Obtain adjusted FPKM/logcpm residual matrix from synapse
```{r data.download}
original.residuals.id = c('ROSMAP' = 'syn5581268', 'MAYO' = 'syn6088523', 'MSSM' = 'syn6120103')
all.used.ids = original.residuals.id
original.residuals = lapply(original.residuals.id, downloadFile)
original.residuals.cor = lapply(original.residuals, function(x){cor(t(x[,-(1:2)]))})

h = mapply(function(x,y){ hist(x, main = y) }, original.residuals.cor,  names(original.residuals.cor), SIMPLIFY = F)
writeLines('Adjusted residuals of original data deposited from the individual sites')
plot(h[[1]], main = names(original.residuals.cor)[1])
plot(h[[2]], main = names(original.residuals.cor)[2])
plot(h[[3]], main = names(original.residuals.cor)[3])
```
#### Obtain adjusted residual matrix from reprocessed counts in synapse
```{r data.download2}
reproc.residuals.id = c('ROSMAP' = 'syn6114451', 'MAYO' = 'syn6128271', 'MSSM' = 'syn6131415')
all.used.ids = c(all.used.ids, reproc.residuals.id)
reproc.residuals = lapply(reproc.residuals.id, downloadFile)
reproc.residuals.cor = lapply(reproc.residuals, function(x){cor(t(x[,-(1:3)]))})

@@

save(list = ls(), file = 'investigate.RData')
obj = File(file = 'investigate.RData', name = 'RNASeq Reprocessing Coexpression Quality Control', parentId = CODE$properties$id)
obj = synStore(obj, activityName = activityName, used = as.character(all.used.ids), executed = thisFile)
```

>>>>

library(Vennerable)
synapseLogin()

options(xtable.type="html")

knitr::opts_chunk$set(
  echo=FALSE,
  warning=FALSE,
  message=FALSE,
  error = FALSE,
  tidy = FALSE,
  cache = FALSE)
```
### Data download
#### Obtain adjusted FPKM/logcpm residual matrix from synapse
```{r data.download, cache = F}
original.residuals.id = c('ROSMAP' = 'syn5581268', 'MAYO' = 'syn6088523', 'MSSM' = 'syn6120103')
all.used.ids = original.residuals.id
original.residuals = lapply(original.residuals.id, downloadFile)
original.residuals.cor = lapply(original.residuals, function(x){cor(t(x[,-(1:2)]))})

h = mapply(function(x,y){ hist(x, main = y) }, original.residuals.cor,  names(original.residuals.cor), SIMPLIFY = F)
writeLines('Adjusted residuals of original data deposited from the individual sites')
plot(h[[1]], main = names(original.residuals.cor)[1])
plot(h[[2]], main = names(original.residuals.cor)[2])
plot(h[[3]], main = names(original.residuals.cor)[3])
```
#### Obtain adjusted residual matrix from reprocessed counts in synapse
```{r data.download2, cache=F}
reproc.residuals.id = c('ROSMAP' = 'syn6114451', 'MAYO' = 'syn6128271', 'MSSM' = 'syn6131415')
all.used.ids = c(all.used.ids, reproc.residuals.id)
reproc.residuals = lapply(reproc.residuals.id, downloadFile)
reproc.residuals.cor = lapply(reproc.residuals, function(x){cor(t(x[,-(1:3)]))})

@@

save(list = ls(), file = 'investigate.RData')
# system('zip investigate investigate.RData')
# obj = File('./InvestigateCoexpIssue.Rmd', name = 'RNASeq Reprocessing Coexpression Quality Control', parentId = CODE$properties$id)
# obj = synStore(obj, activityName = activityName, used = as.character(all.used.ids), executed = thisFile)
```
